Opportunities for improvement in the care of adult trauma patients arriving in shock

### 2024-11-18 thesis.Rmd
test av olika tabell format

The variable with most missing data is ... which lack the data for ... patients.

@@

## Descriptive data

### BE classification
The study demographics median age is `r age` and the most common gender is male, `r male`. Clinically, the median ISS is (...) which is class (...), median INR is (...), and the most common Preinjury ASA class is (...), at (...)%.

```{r sample-characteristics BE, echo=FALSE}
sample.characteristics.tableBE
```
### SBP classification
The study demographics median age is `r age` and the most common gender is male, `r male`. Clinically, the median ISS is (...) which is class (...), median INR is (...), and the most common Preinjury ASA class is (...), at (...)%.

Table 3, 4, 5 present the sample characteristics.

@@

>>>>

The variable with most missing data is BE which lack the data for 1721 patients.

@@

## Descriptive data
The study demographics median age is `r age` and the most common gender is male, `r male`. Clinically, the median ISS is (...) which is class (...), median INR is (...), and the most common Preinjury ASA class is (...), at (...)%.

```{r sample-characteristics BE, echo=FALSE}
sample.characteristics.tableBE
```

@@

```{r ofitable, echo=FALSE, results='asis'}
library(kableExtra)

ofi_table %>%
  kbl(
    col.names = c("BE Shock Class", "OFI Category", "Count", "Percentage (%)"),
    caption = "Counts and Percentages of OFI Broad Categories by BE Shock Class"
  ) %>%
  kable_classic(full_width = FALSE) %>%
  row_spec(0, bold = TRUE) %>% # Optional: Makes header bold
  group_rows(index = table(ofi_table$BE_class)) # Automatically merges BE_class rows

```

```{r combined_ofitable, echo=FALSE, results='asis'}
library(kableExtra)

combined_table %>%
  kbl(
    col.names = c(
      "BE Shock Class",
      "OFI Category",
      "BE Count",
      "BE Percentage (%)",
      "SBP Shock Class",
      "SBP Count",
      "SBP Percentage (%)"
    ),
    caption = "Counts and Percentages of OFI Broad Categories by BE and SBP Shock Classes"
  ) %>%
  kable_classic(full_width = FALSE) %>%
  row_spec(0, bold = TRUE) # Optional: Makes header bold

```
